Conflict-Free Vertex Coloring of Planar Graphs

### 2017-04-13 presentation/presentation.tex
Making some fixes to the presentation

\usepackage{graphicx}
\usepackage[scale=2]{ccicons}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{algorithm, caption}
\usepackage[noend]{algpseudocode}
\usepackage[absolute,overlay]{textpos}
\usepackage{calc}
\usepackage[backend=bibtex,citestyle=authortitle]{biblatex}

@@

@@

  \begin{frame}
    \begin{figure}[h]
      \centering
      \includegraphics[width=14cm]{../figures/map-no-colors-3.pdf}
    \end{figure}
  \end{frame}

@@

    \only<1-2>{
      \begin{itemize}
        \item<1-2> A \textbf{graph} is a set of vertices \emph{V} and a set of edges \emph{E}.
        \pause
        \item A \textbf{planar graph} is a graph that can be drawn on a plane such that no edges overlap.
      \end{itemize}
    }

    \only<3-5>{
      \begin{itemize}
        \item<3-5> The \textbf{neighborhood} of a vertex $v$ is a set of all vertices adjacent to $v$ plus $v$ itself.
        \only<3>{\item<4> Example: The neighborhood of vertex 1: $\{1, 2, 5\}$.}
        \only<4>{\item<4> Example: The neighborhood of vertex 1: $\{1, 2, 5\}$.}
        \only<5>{\item<5> Example: The neighborhood of vertex 5: $\{1, 2, 4, 5, 6\}$.}
      \end{itemize}
    }

    \only<6-8>{
      \begin{itemize}
        \item The \textbf{distance} is the smallest number of edges needed to cross to get from vertex $v$ to vertex $u$.
        \only<6>{\item<7> Example: Distance from vertex 1 to 3: \textbf{2}.}
        \only<7>{\item<7> Example: Distance from vertex 1 to 6: \textbf{2}.}
        \only<8>{\item<8> Example: Distance from vertex 3 to 4: \textbf{3}.}
      \end{itemize}
    }

    \only<9-10>{
      \begin{itemize}
        \item A \textbf{distance-3-set} is a set containing all vertices that have exactly distance 3 from each other.
        \only<9>{\item<7> Example: Distance from vertex 1 to 3: \textbf{2}.}
        \only<10>{\item<10> Example: The only possible distance-3-set: $\{3, 4\}$.}
      \end{itemize}
    }

    \only<11-13>{
      \begin{itemize}
        \item A \textbf{dominating set} is a subset of vertices $D$ of $V$ such that every vertex \emph{not} in $D$ is adjacent to at least one vertex in $D$.
        \only<11>{\item<7> Example: The neighborhood of vertex 1: $\{1, 2, 5\}$.}
        \only<12>{\item<12> Example: $\{2, 5\}$}
        \only<13>{\item<13> Example: $\{2, 4\}$}
      \end{itemize}
    }

@@

    \vspace{4cm}
    \vfill

    \begin{itemize}
      \item A proper \textbf{vertex coloring} of a graph $G$ assigns colors to \emph{every} vertex such that no two adjacent vertices share the same color.
      \pause
      \item The \textbf{chromatic number} of $G$ is the minimum number of colors needed to properly color $G$.
    \end{itemize}
  \end{frame}

@@

    \vspace{4cm}
    \vfill

    \begin{itemize}
      \item<1-2> A \textbf{conflict-free coloring} of a graph $G$ assigns colors to \emph{some} vertices such that there is a uniquely colored vertex within the neighborhood of every vertex.
      \item<2> Every proper vertex coloring of $G$ is also a conflict-free coloring of $G$ as every vertex $v$ would be a unique color itself in its neighborhood.
    \end{itemize}
  \end{frame}

@@

  \section{CF Coloring for General Graphs}
  \subsection{Guaranteeing k-Colorability}
  \begin{frame}
    \frametitle{Guaranteeing Conflict-Free k-Colorability}

>>>>

\usepackage{graphicx}
\usepackage[scale=2]{ccicons}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{algorithm, caption}
\usepackage[noend]{algpseudocode}
\usepackage[absolute,overlay]{textpos}
\usepackage{calc}
\usepackage[backend=bibtex,citestyle=authortitle]{biblatex}
\usepackage[no-math]{fontspec}

@@

\setsansfont[ItalicFont={Fira Sans Light Italic},%
             BoldFont={Fira Sans Bold},%
             BoldItalicFont={Fira Sans Italic}]%
            {Fira Sans Light}

@@

  \begin{frame}
    \begin{figure}[h]
      \centering
      \includegraphics[width=14cm]{../figures/map-no-colors-1.pdf}
    \end{figure}
  \end{frame}

@@

    \only<1-2>{
      \begin{itemize}
        \item<1-2> \textbf{Simple graph}: undirected graph with no loops.
        \pause
        \vfill
        \item \textbf{Planar graph}: no edges overlap.
      \end{itemize}
    }

    \only<3-5>{
      \begin{itemize}
        \item<3-5> \textbf{Neighborhood} of a vertex $v$: a set of all vertices adjacent to $v$ plus $v$.
        \vfill
        \only<3>{\item<4> Example: The neighborhood of vertex 1: $\{1, 2, 5\}$.}
        \only<4>{\item<4> Example: The neighborhood of vertex 1: $\{1, 2, 5\}$.}
        \only<5>{\item<5> Example: The neighborhood of vertex 5: $\{1, 2, 4, 5, 6\}$.}
      \end{itemize}
    }

    \only<6-8>{
      \begin{itemize}
        \item \textbf{Distance}: smallest number of edges to get from one vertex to another.
        \vfill
        \only<6>{\item<7> Example: distance from vertex 1 to 3: \textbf{2}.}
        \only<7>{\item<7> Example: distance from vertex 1 to 6: \textbf{2}.}
        \only<8>{\item<8> Example: distance from vertex 3 to 4: \textbf{3}.}
      \end{itemize}
    }

    \only<9-10>{
      \begin{itemize}
        \item \textbf{Distance-3-set}: contains all vertices with exactly distance 3 from each other.
        \vfill
        \only<9>{\item<7> Example: Distance from vertex 1 to 3: \textbf{2}.}
        \only<10>{\item<10> Example: The only possible distance-3-set: $\{3, 4\}$.}
      \end{itemize}
    }

    \only<11-13>{
    \vspace{0.55cm}
      \begin{itemize}
        \item \textbf{Dominating set}: a subset of vertices $D$ of $V$ such that every vertex \emph{not} in $D$ is adjacent to at least one vertex in $D$.
        \vfill
        \only<11>{\item<7> Example: The neighborhood of vertex 1: $\{1, 2, 5\}$.}
        \only<12>{\item<12> Example: $\{2, 5\}$}
        \only<13>{\item<13> Example: $\{2, 4\}$}
      \end{itemize}
    }

@@

    \vspace{4.5cm}
    \vfill

    \begin{itemize}
      \item A \textbf{proper vertex coloring} of a graph $G$ assigns colors to \emph{every} vertex such that no two adjacent vertices share the same color.
      \pause
      \vfill
      \item The \textbf{chromatic number} of $G$ is the minimum number of colors needed to properly color $G$.
    \end{itemize}
  \end{frame}

@@

    \vspace{4.5cm}
    \vfill

    \begin{itemize}
      \item<1-2> A \textbf{conflict-free coloring} of a graph $G$ assigns colors to \emph{some} vertices such that the neighborhood of every vertex contains at least one unique color.
      \vfill
      \pause
      \item<2> Proper vertex colorings are also conflict-free colorings.
    \end{itemize}
  \end{frame}

@@

  \section{Coloring for General Graphs}
  \subsection{Guaranteeing k-Colorability}
  \begin{frame}
    \frametitle{Guaranteeing Conflict-Free k-Colorability}
